Numerical investigation of the low-load operating protocol of a 620MWe sub-critical power boiler through co-simulation

### 2021-09-28 PAPER_2/PAPER_2_REV1.tex
Update 28/09/2021

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Low load operating protocol investigation of a 620MWe power boiler using an indirectly coupled process model}

@@

\begin{abstract}

Low load operation of utility boiler
ghfbksbv\\
sfjvnsfjlvl\\
kfnmvknsfklvns\\
lk;sfvnsfnvsd\\
sk,vnsfk;nvk;sdv\\
ksdnv;sdv\\
sknvk
\end{abstract}

\begin{keyword}
CFD\sep Eulerian-Eulerian\sep Boiler \sep Low-load operation
\end{keyword}

\end{frontmatter}

@@

\nomenclature[B]{$\epsilon$}{Emissivity \nomunit{$-$}}

@@

The use of coal fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change. However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 $\%$ of the energy needs being met using CFPPs \cite{eskom}. The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol. This will inherently mean CFPPs will need to operate at low-loads for continuous time periods.

@@

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 $\%$. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions. However, to the best the authors' knowledge, no integration of 1-D thermal-hydraulic model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.

@@

The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler. Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $^\circ C$.

@@

\section{Mathematical model}
In this section the modelling techniques used by the study are elaborated. A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution. Following this is a description of the heat transfer modelling techniques and the ends with a description of the process modelling configuration.
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\\
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}\\
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
\\
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}       
\begin{tabular}{lll}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Heat transfer modelling modelling}
The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved sing the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 MWe CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation (G - [$W/m^2$]), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

@@

The process model of the boiler configuration is shown in Figure \ref{fig_flownex}. The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH). The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH) are inlets and outlets.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{FLOWNEX_SETUP}
\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
\label{fig_flownex}
\end{figure}

The heat load results of the CFD simulation for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}. 
\newpage
\subsection{Model inputs}
Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).\\
\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\vspace{5mm}
\label{tbl_fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
\hline
\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
\hline
\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
Carbon & $0.7753$ & $kg/kg_{fuel}$\\
Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
Ash & $0.4090$ & $kg/kg_{fuel}$\\
Moisture & $0.0550$ & $kg/kg_{fuel}$\\
\hline
\textbf{Energy content - (DAF)} & \textbf{Value} &\\
\hline
Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
\hline
\end{tabularx}}
\end{table}

For a 32\% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.  For this study six cases are simulated in total with the following three burner firing configurations being utilized:
\begin{enumerate}
\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
\item Middle front and rear row burners are fired (Case 2 \& Case 5)
\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
\end{enumerate}

@@

\section{Results \& discussion}
The current section will discuss the results obtained from using the above-mentioned modelling methodologies. The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100\%, 80\% and 60\% MCR loads) to that of the experimentally obtained results of the actual plant. Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.

\subsection{Model validation}\label{sec_model_valid}
The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\%. The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.

@@

The CFD model was further validated by comparing the $CO_{ppm}$ and $X_{O_{2}}$ measurements against the CFD results. The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during a full load (100\% MCR) operating conditions. The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$].\\
\begin{figure}[h!]
\centering
\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{COPPM_VALID}}
\hspace{5mm}
\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
\caption{Experimentally calculated $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentration predictions}
\label{fig_probe_valid}
\end{figure}
Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions. It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
\newpage
\subsection{Simulation results for various burner firing arrangements at 32\% MCR }
The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively. With only the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake. This is further exaggerated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies. The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}). This leads to the highest steam generation rate and boiler efficiency as shown in Table \ref{tbl_process_parameters}.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.45]{CO_MF_KEY} [$X_{CO}$] \\
\subfigure[Case 1]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
\subfigure[Case 2]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
\subfigure[Case 3]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
\subfigure[Case 4]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
\subfigure[Case 5]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
\subfigure[Case 6]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 K}
\label{fig_cfd_coppm}
\end{figure}

@@

The mixed firing arrangement, of case 3 and 6, exhibits the best boiler utilization efficiency overall. A 4.8 \% decrease in unburnt carbon percentage is observed when operating using case 3 in relation to case 6. The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $^\circ C$, allowing for better control.

>>>>

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Numerical investigation of the low-load operating protocol of a 620MWe sub-critical power boiler through co-simulation}

@@

\begin{abstract}
This paper uses co-simulation techniques which incorporate a computational fluid dynamic (CFD) model together with a process level model to investigate the low-load operation of a 620 $MWe$ sub-critical boiler. A 1D discretized two-phase model of the water/steam circuit of the furnace, the radiant superheaters (SH) and the convective/back pass heat exchangers was developed. This was coupled with a detailed CFD model incorporating the furnace and radiant superheaters using an Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, the water/steam side effects and the radiant heat exchanger operational limits for six burner firing arrangements for a minimal boiler load of 32 \%. The results show that certain firing arrangements can lead to a high possibility of fire-side corrosion and the over-heating of heat exchanging components. Based on the numerical simulations carried out in terms of obtaining combustion stability, a favourable boiler utilization efficiency and the safe operation of heat exchanging components, a mixed firing arrangement accompanied with a higher secondary air (SA) mass flow-rate for non-firing burners was selected as the best case for the boiler under investigation.
\end{abstract}

\begin{keyword}
CFD\sep Boiler \sep Low-load operation \sep Co-simulation
\end{keyword}
\newpage
\end{frontmatter}

@@

\nomenclature[B]{$\epsilon_p$}{Particle emissivity \nomunit{$-$}}

@@

The use of coal fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change. However, the switch to more sustainable generation sources pose great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resource present in South Africa CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}. The promising integration of renewable energy and the decommissioning of old CFPPs in South Africa, will push CFPP from a primarily base load operation to a mid-merit/flexible operating protocol. This will inherently mean CFPPs will need to operate at low-loads for continuous time periods.

@@

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions. However, to the best the authors' knowledge, no integration of 1-D thermal-hydraulic model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.

@@

The current work proposes the use of CFD modelling methodology to investigate the low-load operational combustion conditions and optimal burner firing arrangement of 620 $MWe$ two-pass sub-critical boiler. Furthermore a process model of boilers entire system, including the furnace up till the secondary air-heater, was modelled, which was indirectly coupled to the CFD model, to investigate the necessary process controls needed to ensure; an adequate boiler utilization efficiency, sufficient attemperation/cooling of the radiant SH's and an exit main steam temperature supply of 535 $[^\circ C]$.

@@

\section{Mathematical model}
In this section the modelling techniques used by the study are elaborated. A description of the CFD modelling configuration is discussed focusing on the fluid flow, turbulence and combustion modelling as well as the particle transport field resolution. Following this is a description of the heat transfer modelling techniques and the ends with a description of the process modelling configuration.
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density is defined present as follows;
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

@@

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabular}{lll}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Heat transfer modelling modelling}
The radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved sing the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

@@

The process model of the boiler configuration is shown in Figure \ref{fig_flownex}. The process model includes all the heat exchanging components up till and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH). The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{FLOWNEX_SETUP}
\caption{Process model of boiler set-up including the downstream convective components using Flownex SE 2021}
\label{fig_flownex}
\end{figure}

The heat load results of the CFD simulation for the furnace, platen and final SH walls were used as inputs the process model as seen in Figure \ref{fig_flownex}. 
\newpage
\subsection{Model inputs}
Table \ref{tbl_fuel} presents the coal characteristics utilized in the current study along with the coals higher heating value (HHV).\\
\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\vspace{2mm}
\label{tbl_fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
\hline
\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
\hline
\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
Carbon & $0.7753$ & $kg/kg_{fuel}$\\
Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
Ash & $0.4090$ & $kg/kg_{fuel}$\\
Moisture & $0.0550$ & $kg/kg_{fuel}$\\
\hline
\textbf{Energy content - (DAF)} & \textbf{Value} &\\
\hline
Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
\hline
\end{tabularx}}
\end{table}

For a 32 \% boiler load the current operational protocol is the to use the bottom front and rear burner rows to meet the low-load demand during start-up.  For this study six cases are simulated in total with the following three burner firing configurations being utilized:
\begin{enumerate}
\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
\item Middle front and rear row burners are fired (Case 2 \& Case 5)
\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
\end{enumerate}

@@

\section{Results \& discussion}
The current section will discuss the results obtained from using the above-mentioned modelling methodologies. The validity of the modelling approach will first be established by comparing the simulation results for MCR load cases (namely 100 \%, 80 \% and 60 \% MCR loads) to that of the experimentally obtained results of the actual plant. Once the model has been shown to demonstrate sufficient accuracy in determining the overall heat loads and combustion characteristics in the boiler furnace at varying loads, the results of the various low-load burner firing configurations are shown and discussed.

\subsection{Model validation}\label{sec_model_valid}
The validation of the proposed model was conducted for three steady-state MCR loads of 100 \%, 80 \% and 60 \%. The model inputs and boundary conditions can be obtained from the study conducted by Laubscher and Rousseau \citep{Laubscher2019b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.

@@

The CFD model was further validated by comparing the $CO_{ppm}$ and $X_{O_{2}}$ measurements against the CFD results. The probe measurements were taken at a furnace height of 37.5 [$m$] near the center of the boiler during a full load (100\% MCR) operating conditions. The probe is inserted from the side walls to a depth of 4.5 [$m$], measurements were taken every 0.5 [$m$].\\
\begin{figure}[h!]
\centering
\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{COPPM_VALID}}
\hspace{5mm}
\subfigure[]{\includegraphics[width = 0.45\textwidth, height =4cm ]{XO2_VALID}}
\caption{Experimentally calculated $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentration predictions}
\label{fig_probe_valid}
\end{figure}

Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions. It can be seen that the CFD model can sufficiently resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location.
\newpage
\subsection{Simulation results for various burner firing arrangements at 32\% MCR }
The temperature and velocity profiles for the various firing arrangements are shown in Figures \ref{fig_cfd_temp} and \ref{fig_cfd_velo} respectively. With only the middle burner rows firing (Cases 2 and 5) a substantial cold region is formed in the lower half the furnace, resulting in the lowest heat uptake. This is further exaggerated when considering Table \ref{tbl_process_parameters} where it is illustrated that the mid-firing arrangements produce the lowest steam flow rates resulting in the lowest boiler efficiencies. The bottom firing arrangement (Cases 1 and 4) results in a high temperature zone located in the bottom half on the burner, while the mixed firing arrangement (Cases 3 and 6) results is an even distribution of high temperature gases across the furnace domain (Figure \ref{fig_cfd_temp}). This leads to the highest steam generation rate and boiler efficiency as shown in Table \ref{tbl_process_parameters}.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.45]{CO_MF_KEY} [$X_{CO}$] \\
\subfigure[Case 1]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT_ISO_COPPM_F}
				\includegraphics[height = 7cm]{BOT_ISO_COPPM_S}}
\subfigure[Case 2]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID_ISO_COPPM_F}
				\includegraphics[height = 7cm]{MID_ISO_COPPM_S}}
\subfigure[Case 3]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM_ISO_COPPM_F}
				\includegraphics[height = 7cm]{FBRM_ISO_COPPM_S}}\\
\subfigure[Case 4]{	\includegraphics[width=0.18\textwidth, height = 7cm]{BOT05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{BOT05_ISO_COPPM_S}}
\subfigure[Case 5]{	\includegraphics[width=0.18\textwidth, height = 7cm]{MID05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{MID05_ISO_COPPM_S}}
\subfigure[Case 6]{	\includegraphics[width=0.18\textwidth, height = 7cm]{FBRM05_ISO_COPPM_F}
				\includegraphics[height = 7cm]{FBRM05_ISO_COPPM_S}}\\
\caption{CO molar fraction ($X_{CO}$) concentrations for cases 1 through 6 [(a)-(f)] on a temperature iso-surface of 1600 [K]}
\label{fig_cfd_coppm}
\end{figure}

@@

The mixed firing arrangement, of case 3 and 6, exhibits the best boiler utilization efficiency overall. A 4.8 \% decrease in unburnt carbon percentage is observed when operating using case 3 in relation to case 6. The predicted re-heater exit steam temperature of case 3 is substantially closer to the desired the temperature of 535 $[^\circ C]$, allowing for better control.
